**Reading the data**

```{r}
monitor <- read.csv("activity.csv", stringsAsFactors = FALSE)
head(monitor)
```

**The mean of total number of steps taken per day**

```{r}
library("dplyr")
totalSteps <- monitor %>% group_by(date) %>% summarise(total = sum(steps, 
    na.rm = T)) 

# Define total mean and total median of steps sums for each day
totalMean <- mean(totalSteps$total)
print(totalMean)

totalMedian <- median(totalSteps$total)
print(totalMedian)

library("ggplot2")
theme_set(theme_gray(base_size = 14))
ggplot(totalSteps, aes(x = total)) + geom_histogram(fill = "yellow", 
    colour = "black") + geom_vline(xintercept = totalMean, color = "brown", 
    linetype = "dashed", size = 1) + geom_vline(xintercept = totalMedian, color = "red", 
    linetype = "dashed", size = 1) + labs(title = "Number of steps \n taken for each day") + 
    labs(x = "", y = "")
```

**5 Minute interval**
```{r}
avgSteps <- monitor %>% group_by(interval) %>% summarise(avg.intvl = mean(steps, na.rm = T))

maxInd <- which(avgSteps$avg.intvl == max(avgSteps$avg.intvl))
maxInterv <- avgSteps[maxInd, 1]

qplot(interval, avg.intvl, data = avgSteps) + geom_line() + geom_vline(xintercept = maxInterv, 
    color = "red", linetype = "dashed", size = 1) + labs(title = "Time series ") + 
    labs(x = "5-minute interval signature", y = "number of steps ")